\documentclass[11pt]{article}
% Command line: pdflatex -shell-escape compulse.tex
\usepackage{geometry} 
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{times}
\usepackage{bm}
\usepackage{fixltx2e}
\usepackage[outerbars]{changebar}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{color}
\usepackage{tabularx}
\usepackage{ulem}
\usepackage{verbatim}
\usepackage{textcomp}

\epstopdfsetup{suffix=} % to remove 'eps-to-pdf' suffix from converted images
%\usepackage{todonotes} % use option disable to hide all comments

\usepackage[sort&compress]{natbib}
\bibpunct{[}{]}{,}{n}{,}{,}

\usepackage[noend]{algpseudocode}

\usepackage{dsfont}
\usepackage{relsize}

\usepackage{todonotes}

\graphicspath{{Figure/}}

%changing the Eq. tag to use [] when numbering. use \eqref{label} to reference equations in text.
\makeatletter
  \def\tagform@#1{\maketag@@@{[#1]\@@italiccorr}}
\makeatother

\linespread{1.5}
%\setlength{\parindent}{0in}

% the following command can be used to mark changes made due to reviewers' concerns. Use as \revbox{Rx.y} for reviewer x, concern y.
\newif\ifmarkedup
\markeduptrue

\ifmarkedup
	\newcommand{\revbox}[1]{\marginpar{\framebox{\textcolor{blue}{#1}}}}
\else
	\newcommand{\revbox}[1]{}
	\renewcommand{\textcolor}[1]{}
	\renewcommand{\sout}[1]{}
\fi

%\newcommand{\bop}{$\vert B_1^+ \vert$}
\newcommand{\kt}{$k_\textrm{T}$}
\newcommand{\bmap}{$B_1^+$}
\newcommand{\mytilde}{\raise.17ex\hbox{$\scriptstyle\mathtt{\sim}$}}  % tilde symbol
\mathchardef\mhyphen="2D

\begin{document}

\title{k-Space Domain Parallel Transmit Pulse Design}
\author{Jun Ma$^{1,2}$, Bernhard Gruber$^{3,4}$, Xinqiang Yan$^{1,5}$, and William A. Grissom$^{1,2,5*}$}
\maketitle
\begin{flushleft}
$^1$Vanderbilt University Institute of Imaging Science, Nashville, TN, United States\\
$^2$Department of Biomedical Engineering, Vanderbilt University, Nashville, TN, United States\\
$^3$A. A. Martinos Center for Biomedical Imaging, Massachusetts General Hospital, Harvard Medical School, Charlestown, MA, United States\\
$^4$Division MR Physics, Center for Medical Physics and Biomedical Engineering, Medical University Vienna, Vienna, Austria\\
$^5$Department of Radiology and Radiological Sciences, Vanderbilt University, Nashville, TN, United States\\    

\par
-------------------------- 

\par
Word Count: Approximately 3550 \\
*Corresponding author: \\
Will Grissom\\
Department of Biomedical Engineering\\
Vanderbilt University\\
5824 Stevenson Center\\
Nashville, TN 37235 USA \\
E-mail: will.grissom@vanderbilt.edu \\
Twitter: @wgrissom

\par Submitted to Magnetic Resonance in Medicine for consideration as a Full Paper.

\par
Acknowledgment: This work was supported by NIH grants R01 EB016695 and U01 EB 025162.

\end{flushleft}
\thispagestyle{plain}

\pagebreak

%%%%%%%%%%%%%%%%%%%%%%% Abstract %%%%%%%%%%%%%%%%%%%%%%%

\section*{\underline{Abstract}} 
{\bf Purpose:}
To accelerate the design of multidimensional parallel transmission pulses. 
\\[1em]
{\bf Methods:}
A k-space domain parallel transmission pulse design algorithm was proposed that
produces a sparse matrix relating a target excitation pattern to the pulses that produce it,
and can be finely parallelized. 
The algorithm was applied in simulations to the design of 3D SPINS pulses for inner volume excitation in the brain at 7 Tesla.
It was characterized in terms of the dependence of computation time, excitation error, and required memory
on algorithm parameters,
and it was compared to the spatial domain pulse design method in terms computation time, excitation error,
Gibbs ringing, and ability to compensate off-resonance.
\\[1em]
{\bf Results:}
The proposed algorithm achieved approximately 90\% faster pulse design compared to 
an iterative spatial domain method, with the same number of parallel threads,
with the tradeoff of increased excitation error and RMS RF amplitude. 
It reduced the memory required to store the design matrix by 98\% compared to a full matrix solution.
Even with a coarse design grid, the algorithm produced patterns that were free of Gibbs ringing.
It was similarly sensitive to k-space undersampling as the spatial domain method,
and was similarly capable of compensating for off-resonance.
\\[1em]
{\bf Conclusion:}
The proposed k-space domain algorithm accelerates and finely parallelizes parallel transmission pulse design,
with a modest tradeoff of excitation error and RMS RF amplitude.
\\[1em]
{\bf \noindent Key words:} Parallel Transmission; RF pulses; Ultra-high field MRI; RF pulse design; Selective excitation.

\pagebreak

%%%%%%%%%%%%%%%%%%%%%%% Main Text %%%%%%%%%%%%%%%%%%%%%%%

\input{Introduction}

\input{Theory}

\input{Method}

\input{Result}

\input{Conclusion}



\pagebreak

\bibliographystyle{unsrt}  % cse doesn't work
\bibliography{kPtx_paper}

\pagebreak








\end{document}